\textbf{Transparency to hybrid open access through publisher-provided metadata: An article-level study of Elsevier}

### 2021-05-10 analysis/manuscript.Rmd
subject field naming

```{r}
subject_all_years <- hybrid_subject %>% 
  ungroup() %>% 
  group_by(issn, description, subject_area) %>% 
  summarise(n_oa = sum(oa),
            n = sum(articles)) %>%
  ungroup() %>%
  group_by(description) %>%
  filter(subject_area != "Multidisciplinary")

@@

```{r oa_sub_uptake, fig.cap='Open access (OA) uptake in Elsevier hybrid journals in percent grouped by subject area and field between 2015-19. Visualized as a box-and-whiskers plot limited to an OA share of 20\\%; the red line represents the overall median (2.5), jittered dots represent individual journals. Subject fields are ordered based on the median OA uptake.', fig.asp=1.3, out.width="90%"}
# with labels
subject_all_years <- 
  inner_join(subject_all_years, subject_area_all_jn, by = "subject_area") %>%
  mutate(subject_area = glue::glue("{subject_area} ({journals_n} Journals)"))

p_subject <- ggplot(subject_all_years, aes(fct_reorder(description, n_oa / n, .fun = median), n_oa / n)) + 
  geom_boxplot(aes(color = subject_area)) +
  geom_jitter(alpha = .05, aes(color = subject_area), size = 1) +
  facet_wrap(~subject_area, scales = "free_y", nrow = 4) +
  geom_hline(yintercept = median_all,  colour = "red", linetype ="dashed", size = 1) +
  scale_colour_manual(NULL, values = c("#7F3C8D", "#11A579", "#3969AC", "#F2B701"),
                      guide=FALSE) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 5L),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip(ylim=c(0,0.2)) +
  labs(x = NULL, y = "Five-Year Hybrid OA Uptake Rate\nper Journal") +
  theme_minimal_vgrid(font_size = 10) +
  theme(strip.text = element_text(face="bold"))
p_subject
```

@@

@@

>>>>

```{r}
subject_all_years <- hybrid_subject %>% 
  ungroup() %>% 
  group_by(issn, description, subject_area) %>% 
  summarise(n_oa = sum(oa),
            n = sum(articles)) %>%
  ungroup() %>%
  group_by(description) %>%
  filter(subject_area != "Multidisciplinary")
# distinct journals per subject
journals_per_subject <- subject_all_years %>%
  summarise(n_journals = n_distinct(issn)) %>%
  mutate(field_label = glue::glue("{description} (n={n_journals})"))

@@

```{r oa_sub_uptake, fig.cap='Open access (OA) uptake in Elsevier hybrid journals in percent grouped by subject area and field between 2015-19. Visualized as a box-and-whiskers plot limited to an OA share of 20\\%; the red line represents the overall median (2.5), jittered dots represent individual journals. Subject fields are ordered based on the median OA uptake.', fig.asp=1.3, out.width="90%"}
# with labels
subject_all_years_ <- 
  inner_join(subject_all_years, journals_per_subject, by = "description")

p_subject <- ggplot(subject_all_years_, aes(fct_reorder(field_label, n_oa / n, .fun = median), n_oa / n)) + 
  geom_boxplot(aes(color = subject_area)) +
  geom_jitter(alpha = .05, aes(color = subject_area), size = 1) +
  facet_wrap(~subject_area, scales = "free_y", nrow = 4) +
  geom_hline(yintercept = median_all,  colour = "red", linetype ="dashed", size = 1) +
  scale_colour_manual(NULL, values = c("#7F3C8D", "#11A579", "#3969AC", "#F2B701"),
                      guide=FALSE) +
  scale_y_continuous(
    labels = scales::percent_format(accuracy = 5L),
    expand = expansion(mult = c(0, 0.05))
  ) +
  coord_flip(ylim=c(0,0.2)) +
  labs(x = NULL, y = "Five-Year Hybrid OA Uptake Rate\nper Journal") +
  theme_minimal_vgrid(font_size = 10) +
  theme(strip.text = element_text(face="bold"))
p_subject
```

@@

```{r}
# sector/discipline
hybrid_invoice %>%
  filter(!is.na(`Primary research focus`)) %>%
  count(Sector, `Primary research focus`) %>%
  mutate(prop = n / sum(n) * 100) %>% 
  pivot_wider(id_cols = c("Primary research focus"), names_from = Sector, values_from = n) %>%
  kableExtra::kbl(booktabs = TRUE) %>%
  kable_styling(latex_options = c("scale_down"))

```

@@

```{r ccby_vs_openapc}
ggplot(ind_sponsor_df, aes(in_open_apc, cc_by, size = articles)) +
  geom_point(alpha = 0.5) +
  theme_minimal_grid() +
  scale_x_continuous(limits = c(0,1), labels = scales::percent_format()) +
  scale_y_continuous(limits = c(0,1), labels = scales::percent_format()) +
  labs(y = "CC BY Share", x = "Spending info in Open APC", size = "Invoiced\nOA Articles") +
  theme(legend.position="right", legend.justification = "right")
```

### 2021-05-10 analysis/manuscript.tex
typo
subject field naming

@@

@@

@@

>>>>

\multicolumn{6}{l}{\textbf{Physical Sciences}}\\

@@

\multicolumn{6}{l}{\textbf{Social Sciences}}\\

@@

\begin{table}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrr}
\toprule
Primary research focus & government & higher education & other & private non-profit\\
\midrule
Broad & 2849 & 4003 & NA & 6\\
Health Science & 2706 & NA & 3 & 4678\\
Life Sciences & 2591 & NA & NA & 3\\
Physical Sciences & 5169 & 13 & NA & 14\\
SSH & 1209 & 1 & NA & 1\\
\bottomrule
\end{tabular}}
\end{table}

@@

\begin{center}\includegraphics[width=0.7\linewidth,]{manuscript_files/figure-latex/ccby_vs_openapc-1} \end{center}
